### 2019-09-13 journal/ms.Rmd
revisions

  - id            : "2"
    institution   : "Department of Psychology, University of Illinois"

@@

@@

# Acknowledgements
This work was supported by a post-doctoral grant from the Fyssen Foundation.

>>>>

  - id            : "2"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"

@@

# Appendix

## Edit 1

```{r}
#Import data from saved
data_all <- feather::read_feather("../saved_data/data_static_scaled_edit1.feather")

data_all$language <- plyr::mapvalues(data_all$language, 
                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))

data_long <- data_all %>%
  rename(Sem = sem_deg, Phono=phono_deg) %>%
  gather(predictor, value, Sem:frequency) %>%
  dplyr::filter(predictor == "Phono")

plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
                                  aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age")

plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age")

corr_plot <- cowplot::plot_grid(
  plot_correlation_1 ,
  plot_correlation_2 ,
  nrow = 1#, 
  #align = 'vh',
  #hjust = -1
)

```{r corrPlot, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}

corr_plot
#plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

```{r}
##Test
static_preds <- feather::read_feather("../saved_data/coefs_all_edit1.feather")

plot_static_preds_edit1 <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7) + #,+
        #axis.text.x = element_text(size=7.5, angle=45)) +
  scale_y_continuous(breaks =c(-1,0,1))  +
  #scale_y_discrete(breaks =NULL)
  ylab("Estimate") +xlab("Mechanism")

```{r staticPredEdit1, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language. Results are shown for both production and comprehension data. Ranges indicate 95\\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).", fig.width=8, fig.height=3}

plot_static_preds_edit1

```{r}
static_preds_all <- feather::read_feather("../saved_data/static_preds_all_edit1.feather")

ggsave("figs/plot_static_preds_all_edit1.pdf", plot = plot_static_preds_all, width = 6, height = 3)

```{r staticAllEdit, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect. Results are shown for both production and comprehension data. Ranges indicate 95\\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.", fig.width=6, fig.height=2.5}

## Continuous edit distance

```{r}
#Import data from saved
data_all <- feather::read_feather("../saved_data/data_static_scaled_nt.feather")

data_all$language <- plyr::mapvalues(data_all$language, 
                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))

data_long <- data_all %>%
  rename(Sem = sem_deg, Phono=phono_deg) %>%
  gather(predictor, value, Sem:frequency) %>%
  dplyr::filter(predictor == "Phono")

plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
                                  aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  #coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age")

plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  #coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age")

corr_plot_nt <- cowplot::plot_grid(
  plot_correlation_1 ,
  plot_correlation_2 ,
  nrow = 1#, 
  #align = 'vh',
  #hjust = -1
)

```{r corrPlotnt, out.width = "\\textwidth", fig.pos = "!h", fig.height=5, fig.cap = "Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients."}

corr_plot_nt
#plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

```{r}
##Test
static_preds <- feather::read_feather("../saved_data/coefs_all_nt.feather")

plot_static_preds_nt <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7) + #,+
        #axis.text.x = element_text(size=7.5, angle=45)) +
  scale_y_continuous(breaks =c(-1,0,1))  +
  #scale_y_discrete(breaks =NULL)
  ylab("Estimate") +xlab("Mechanism")

```{r staticPrednt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the regression model in each language. Results are shown for both production and comprehension data. Ranges indicate 95\\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).", fig.width=8, fig.height=3}

plot_static_preds_nt

```{r}
static_preds_all <- feather::read_feather("../saved_data/static_preds_all_nt.feather")

plot_static_preds_all_nt <- ggplot(static_preds_all, aes(x = predictor, y = Estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = Estimate, col = predictor, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~measure)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

ggsave("figs/plot_static_preds_all_nt.pdf", plot = plot_static_preds_all_nt, width = 6, height = 3)

```{r staticAllnt, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect. Results are shown for both production and comprehension data. Ranges indicate 95\\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.", fig.width=6, fig.height=2.5}

plot_static_preds_all_nt

Problem of colinearity beteen phono and length, that's why the estimates are noisy

## Phonological compostion across languages

generate pair and edit distance, link=1 and link = 2  
Transform the pairs into matrices 
Do pairwise mantel test and draw the distribution

@@

# Acknowledgements
This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.

### 2019-09-13 journal/ms.tex
revisions

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Department of Psychology, Stanford University\\
          \textsuperscript{2} Department of Psychology, University of Illinois  }

@@

@@

This work was supported by a post-doctoral grant from the Fyssen
Foundation.

>>>>

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Department of Psychology, Stanford University\\
          \textsuperscript{2} Department of Brain and Cognitive Sciences, Massachusetts Institute of
Technology  }

@@

\section{Appendix}\label{appendix}

\subsection{Edit 1}\label{edit-1}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlot}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPredEdit1-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression model in each language. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).}\label{fig:staticPredEdit1}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllEdit}
\end{figure}

\subsection{Continuous edit distance}\label{continuous-edit-distance}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlotnt-1} \caption{Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlotnt}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPrednt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression model in each language. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).}\label{fig:staticPrednt}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllnt}
\end{figure}

@@

This work was supported by a post-doctoral grant from the Fyssen
Foundation, NSF \#1528526, and NSF \#1659585.

### 2019-09-13 main_analyses.Rmd
remarks by george
final version
revisions

data_all$language <- plyr::mapvalues(data_all$language, 
                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))

@@

mysummary <- data_all %>%
  group_by(language, measure) %>%
  summarise(min_age = min(age),
            max_age = max(age),
            nouns = n_distinct(item)) %>%
  mutate(age_range = paste(min_age, max_age, sep = "-")) %>%
  select(-min_age, -max_age)  %>%
  group_by(language, measure) %>%
  nest() %>%
  spread(measure, data) %>%
  unnest(.sep = "_") %>%
  select(language, un = understands_nouns, ua=understands_age_range,
                   pn = produces_nouns, pa=produces_age_range)

@@

data_aoa <- data_aoa %>%
  select(language, form, measure, uni_lemma, item, definition, aoa) %>%
  distinct()

#feather::write_feather(data_aoa, "saved_data/data_aoa.feather")

@@

#Save at this point
#feather::write_feather(data_growth, "saved_data/data_growth.feather")
data_growth <- feather::read_feather("saved_data/data_growth.feather") 
```

@@

words_growth <- data_growth %>%
  #filter(!is.na(uni_lemma)) %>% #only keep unilemmas that intersect with free association data
  dplyr::filter(aoa > 5)

@@

  phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang)

  #Threshold the phonetic distance (we take t=2, becuase t=1 is too sparse) 
  threshold <- 2

@@

  phono_growth <- growth_meas_lang %>%
   left_join(phono_PAC) %>%
   left_join(phono_PAT)

@@

phono_red <-  map(growth_by_meas_lang, phono_net_fun) %>%
  bind_rows()

#feather::write_feather(phono_red, "saved_data/phono_red.feather")
phono_red <- feather::read_feather("saved_data/phono_red.feather")

@@

aoa_items <- data_aoa %>%
  select(language, measure, item, aoa) # Here I should round the AoA?

@@

data_static_prop$language <- plyr::mapvalues(data_static_prop$language, 
                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", "Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", "Russian", "Spanish", "Swedish", "Turkish"))

data_static_prop <- data_all %>%
  left_join(data_static_pred) 
```

@@

@@

#Impute missing values and center/scale
uni_scale <- unilemmas %>%
  group_by(measure, language) %>%
  mutate_at(c('sem_deg', 'phono_deg', 'length', 'frequency'), funs(as.numeric(Hmisc::impute(.)))) %>%
  mutate_at(c('sem_deg', 'phono_deg', 'length', 'frequency'), funs(as.numeric(scale(.))))

feather::write_feather(uni_scale, "saved_data/data_static_scaled.feather")
#phono_red <- feather::read_feather("saved_data/phono_red.feather")

@@

@@

```{r fig.width=10, fig.height=5}
plot_correlation_prod <- ggplot(subset(data_long, measure == "produces"), aes(x=value, y=aoa))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="produces"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

@@

@@

@@

  for (i in 1:length(model_list)) {

@@

    while (typeof(posterior_model)=="NULL") {
      posterior_model <- webppl(model_list[[i]],
                                data = data_growth_meas_lang,
                                data_var = "data",
                                inference_opts = list(
                                  method = "MCMC",
                                  samples = 1000, 
                                  burn = 500),
                                model_var = "AOA",
                                output_format = "webppl")
    }

@@

feather::write_feather(posterior, "saved_data/posterior.feather")
posterior <- feather::read_feather("saved_data/posterior.feather")

@@

feather::write_feather(param_summary_all, "saved_data/growth_preds.feather")
param_summary_all <- feather::read_feather("saved_data/growth_preds.feather")

@@

```{r fig.width=5, fig.height=2}
ggplot(subset(param_summary_all, measure == "produces"), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

@@

```{r fig.width=5, fig.height=2}
ggplot(subset(param_summary_all, measure == "understands"), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

@@

@@

feather::write_feather(coefs_all, "saved_data/static_preds.feather")
coefs_all <- feather::read_feather("saved_data/static_preds.feather")

@@

coef_agg_form <- coef_agg_prod %>%
  bind_rows(coef_agg_comp) %>%
  mutate(Test = ifelse(toString(formula[3])=='frequency + length + sem_deg + phono_deg + (1 | language)', 'Combined', 'Individual'))

@@

feather::write_feather(coefs_agg_all, "saved_data/static_preds_all.feather")
coefs_agg_all <- feather::read_feather("saved_data/static_preds_all.feather")

>>>>

@@

#Number of children

#Number of children
n_child <- data_all %>%
  mutate(sum_child =  num_true+num_false) %>%
  group_by(language, measure, item) %>%
  summarise(children = sum(sum_child)) %>%
  distinct(language, measure, children)

mysummary <- data_all %>%
  group_by(language, measure) %>%
  summarise(min_age = min(age),
            max_age = max(age),
            nouns = n_distinct(item)) %>%
  left_join(n_child) %>%
  mutate(age_range = paste(min_age, max_age, sep = "-")) %>%
  select(-min_age, -max_age)  %>%
  group_by(language, measure) %>%
  nest() %>%
  spread(measure, data) %>%
  unnest(.sep = "_") %>%
  select(language, un = understands_nouns, ua=understands_age_range, uc= understands_children,
                   pn = produces_nouns, pa=produces_age_range, pc=produces_children)

@@

feather::write_feather(data_aoa, "saved_data/data_aoa.feather")

aoa <- feather::read_feather("saved_data/data_aoa.feather")  %>%
  select(language, form, measure, uni_lemma, item, definition, aoa) %>%
  distinct()

@@

#Save at this point
#feather::write_feather(data_growth, "saved_data/data_growth.feather")
data_growth <- feather::read_feather("saved_data/data_growth.feather")

@@

words_growth <- data_growth %>%
    #filter(!is.na(uni_lemma)) %>% #only keep unilemmas that intersect with free association data
  filter(age > 5)

@@

  phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang) %>%
    mutate(language = lang) %>%

  #Threshold the phonetic distance (we take t=2, becuase t=1 is too sparse) 
  threshold <- 1

@@

 # phono_nt_PAC <- PAC_generator(vocab_age = growth_meas_lang, word_pairs = phono_pairs %>% IPA_continuous()) #%>% 
 #    rename(PAC_phono = value) %>% select(-definition, -uni_lemma)

  phono_growth <- growth_meas_lang %>%
   left_join(phono_nt_PAC) 
   left_join(phono_PAC) %>%
   left_join(phono_PAT)

  return(phono_growth)
}

phono_red_nt <-  map(growth_by_meas_lang, phono_net_fun) %>%
  bind_rows()

feather::write_feather(phono_red_nt, "saved_data/phono_red_nt.feather")

feather::write_feather(phono_red, "saved_data/phono_red_edit1.feather")
phono_red <- feather::read_feather("saved_data/phono_red_nt.feather")

feather::write_feather(data_growth_net, "saved_data/data_growth_net_nt.feather")

Here do Mantel tests
```{r}

  def_list<- growth_meas_lang %>%
    filter(!is.na(uni_lemma)) %>%
    trim_all_definition() %>% 
    filter(age==first_age) %>%
    select(item, definition)

  item_unilemma <- growth_meas_lang %>%
    filter(!is.na(uni_lemma)) %>%
    select(item, uni_lemma)

  phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang) %>%
    mutate(language = lang) %>%
    left_join(item_unilemma) %>%
    rename(item0 = item,
           item = pair,
           item.uni_lemma = uni_lemma) %>%
    left_join(item_unilemma) %>%
    rename(pair.uni_lemma = uni_lemma,
           pair = item,
           item = item0)

  return(phono_pairs)
}

#Ici mantel test
phono_pairs_all <- map(growth_by_meas_lang, phono_net_fun) %>%
  bind_rows()

feather::write_feather(phono_pairs_all, "saved_data/phono_pairs_all.feather")

phono_pairs_dist <- phono_pairs_all %>%
  mutate(link1 = as.numeric(dist<=1)) %>%
  mutate(link2 = as.numeric(dist<=2)) %>%
  mutate(link_cont = ifelse(dist==0, 1, 1/dist))

#Pairwise comparision: each time, take the overlap and do the test

data_prod <- data_aoa %>%
  filter(measure =='produces')

data_by_lang <- split(phono_pairs_dist$language)

pair_data <- function(lang1){

  pair_cor_data <- function (lang2){

  lang1_unilemmas <- unique(lang1$uni_lemma)
  lang2_unilemmas <- unique(lang2$uni_lemma)
  uni_intersect <-  intersect(lang1_unilemmas, lang2_unilemmas)

  data_lang1 <- lang1 %>%
    filter(!is.na(uni_lemma),
           uni_lemma %in% uni_intersect) %>%
    select(uni_lemma, aoa) %>%
    group_by(uni_lemma) %>%
    summarise(aoa1=mean(aoa))

  data_lang2 <- lang2 %>%
    filter(!is.na(uni_lemma),
           uni_lemma %in% uni_intersect) %>%
    select(uni_lemma, aoa) %>%
    group_by(uni_lemma) %>%
    summarise(aoa2=mean(aoa))

  both <- data_lang1 %>%
    left_join(data_lang2)

  mycorr <- cor.test(rank(both$aoa1), rank(both$aoa2), method = 'kendall')
  val=mycorr$estimate
  p=mycorr$p.value
  language1 = unique(lang1$language) 
  language2 = unique(lang2$language)

  data.frame(language1=language1, language2=language2, tau=val, sig = p)

}
  map(data_by_lang, pair_cor_data) %>%
    bind_rows()

@@

@@

aoa_items <- aoa %>%
  select(language, measure, item, aoa) # Here I should round the AoA?

@@

data_static_prop <- data_all %>%
  left_join(data_static_pred)

@@

#data_all$language <- plyr::mapvalues(data_all$language, 
#                                 from = c("Croatian","Danish","English (American)", "French (Quebecois)", #"Italian", "Norwegian", "Russian", "Spanish (Mexican)", "Swedish", "Turkish"), 
#                                 to = c("Croatian","Danish","English", "French", "Italian", "Norwegian", #"Russian", "Spanish", "Swedish", "Turkish"))

@@

unilemmas_nt <-unilemmas %>%
  filter(phono_deg != 'Inf')

#Impute missing values and center/scale
uni_scale <- unilemmas_nt %>%
  group_by(measure, language) %>%
  mutate_at(c('sem_deg', 'phono_deg', 'length', 'frequency'), funs(as.numeric(Hmisc::impute(.)))) %>%
  mutate_at(c('sem_deg', 'phono_deg', 'length', 'frequency'), funs(as.numeric(scale(.))))

feather::write_feather(uni_scale, "saved_data/data_static_scaled_nt.feather")
#phono_red <- feather::read_feather("saved_data/phono_red.feather")

@@

Here do some analysis
```{r}
#Regression with phono (edit=1)

#Regression with phono (1/edit)
```

@@

```{r fig.width=10, fig.height=5}
plot_correlation_prod <- ggplot(subset(data_long, measure == "produces"), aes(x=value, y=aoa))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  #coord_cartesian(xlim=c(-1,10))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="produces"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

@@

#data_growth_net <- feather::read_feather("saved_data/data_growth_net.feather")
data_growth_net_as_ws <- feather::read_feather("../asNet_local/saved_data/data_growth_net_AS_WS.feather")

@@

#data_growth_pred_as <- feather::read_feather("../asNet_local/saved_data/data_growth_pred_wg_as_test")

@@

   #for (i in 1:1) {
   for (i in 1:length(model_list)) {

@@

    while (typeof(posterior_model)=="NULL") {
      posterior_model <- webppl(model_list[[i]],
                                data = data_growth_meas_lang,
                                data_var = "data",
                                inference_opts = list(
                                  method = "MCMC",
                                  samples = 500, 
                                  burn = 500),
                                model_var = "AOA",
                                output_format = "webppl")
    }

@@

feather::write_feather(posterior, "saved_data/posterior_as_ws.feather")
#posterior <- feather::read_feather("saved_data/posterior.feather")

#data_growth_meas_lang <- data_growth_by_meas_lang[[1]]

#posterior_fun(data_test)

@@

#feather::write_feather(param_summary_all, "saved_data/growth_preds.feather")
#param_summary_all <- feather::read_feather("saved_data/growth_preds.feather")

@@

```{r fig.width=5, fig.height=2}
ggplot(subset(param_summary_all, measure == "produces" & Test =="Individual"), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

@@

```{r fig.width=5, fig.height=2}
ggplot(subset(param_summary_all, measure == "understands" & Test =="Individual"
              ), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

@@

uni_scale <- feather::read_feather("saved_data/data_static_scaled_nt.feather")
#uni_scale_edit <- feather::read_feather("saved_data/data_static_scaled_edit1.feather")

@@

feather::write_feather(coefs_all, "saved_data/coefs_all_nt.feather")

@@

coef_agg_form <- coef_agg_prod %>%
  bind_rows(coef_agg_comp) %>%
  mutate(Test = ifelse(toString(formula[3])=='frequency + length + sem_deg + head(phono_deg + (1 | language)', 'Combined', 'Individual'))

@@

feather::write_feather(coefs_agg_all, "saved_data/static_preds_all_nt.feather")
coefs_agg_all <- feather::read_feather("saved_data/static_preds_all_nt.feather")
